XS-FACE preliminary analysis

### 2018-01-08 analysis/face_detection_analysis.Rmd
updated csv

Load CSV
```{r, message=FALSE, warning=FALSE}
data <- read_csv('/Users/alessandro/Github/xs-face/data/3.csv')
```

Summarize
```{r}
data %>%
  #filter(w>100 | is.na(w)) %>%
  distinct(group, video, frame, is_face, angle) %>% # ignore > 1 face detections
  group_by(group, angle) %>%
  summarise(face_frames=sum(is_face=="True"), total=n()) %>%
  mutate(percentage=face_frames/total * 100) %>%
  arrange(angle, group) %>%
  kable
```

>>>>

Load CSV
```{r, message=FALSE, warning=FALSE}
data1 <- read_csv('/Users/alessandro/workspace/3.csv')
data <- read_csv("../data/final_output/mtcnn_face_detections.csv")
```

```{r}
setwd("..")
```

Summarize
```{r}
data1 %>%
  #filter(w>100 | is.na(w)) %>%
  distinct(group, video, frame, is_face) %>% # ignore > 1 face detections
  group_by(group) %>%
  summarise(face_frames=sum(is_face=="True"), total=n()) %>%
  mutate(percentage=face_frames/total * 100) %>%
  arrange(group) %>%
  kable
```
